---
title: "Untitled"
author: "hanfu shi"
date: "2021/10/5"
output: html_document
---
```{r}
library(tidyverse)
library(ggridges)

```

##load the weather data
```{r }
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

## Scatterplotes
create my first scatterplot
```{r}
ggplot(weather_df, aes(x= tmin, y = tmax))+
  geom_point()         

```

New approach, same plot.

```{r}
weather_df%>%
  ggplot(aes(x = tmin, y = tmax))+geom_point()
```

Save and edit a plot object.
```{r}
weather_plot =
  weather_df%>%
  ggplot(aes(x = tmin, y = tmax))

weather_plot + geom_point()
```


##advanced scatterplot ...
start with the same one and make it fancy!
```{r}
weather_df%>%
  ggplot(aes(x = tmin, y = tmax,color = name))+geom_point()+
  geom_smooth(se = F)

```


what about the 'aes' placement?
```{r}
weather_df%>%
  ggplot(aes(x = tmin, y = tmax))+geom_point(aes(color = name))+
  geom_smooth(se = F)
# just have one single line, better to add color in ggplot
```

let's facet some things!!
```{r}
weather_df%>%
  ggplot(aes(x = tmin, y = tmax,color = name))+geom_point()+
  geom_smooth(se = F)+
  facet_grid(. ~ name)

weather_df%>%
  ggplot(aes(x = tmin, y = tmax,color = name))+geom_point()+
  geom_smooth(se = F)+
facet_grid(name ~ .)#row
   
```

```{r}
weather_df%>%
  ggplot(aes(x = tmin, y = tmax,color = name))+
  geom_point(alpha= .5,size =.3)+
  geom_smooth(se = F,size= 3)+
  facet_grid(. ~ name)

weather_df%>%
  ggplot(aes(x = tmin, y = tmax,alpha= tmin,color = name))+ #transparancey depedent on variable
  geom_point(size =.3)+
  geom_smooth(se = F,size= 3)+
  facet_grid(. ~ name)
```

let's combine some elements and try a new plot.
```{r}
weather_df%>%
  ggplot(aes(x = date, y=tmax,color = name))+
  geom_point(aes(size= prcp),alpha = .2)+
  geom_smooth(se = F)+
  facet_grid(. ~ name)

```

How many geoms have to exist
##some small notes
you can have whatever geoms you want
```{r}
weather_df %>%
  ggplot(aes(x=tmin, y=tmax, color=name))+
  geom_smooth(se=F)


```


You can use a neat geom!
```{r}
weather_df %>%
  ggplot(aes(x=tmin, y=tmax))+
  geom_density2d()+
  geom_point(alpha=.3)


```


##Univariate plots
Histograms are really great.
```{r}
weather_df %>%
  ggplot(aes(x=tmin))+
  geom_histogram()
```

can we add color..
```{r}
weather_df %>%
  ggplot(aes(x=tmin,fill = name))+
  geom_histogram()+
  facet_grid(. ~ name)
```

let's try a new geomtry
```{r}
weather_df %>%
  ggplot(aes(x=tmin,fill = name))+
  geom_density(alpha=0.3)

```

what about box plots??
```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmin))+
  geom_boxplot()

```


Trendy plots :-)
```{r}
weather_df%>%
  ggplot(aes(x = name, y =tmin, fill = name))+
  geom_violin(alpha = 0.5)+
  stat_summary(fun = "median")

```

Ridge plots -- most polular plot of 2017
```{r}
weather_df%>%
  ggplot(aes(x = tmin, y =name))+
  geom_density_ridges()

```



